My title

### 2024-04-22 paper/paper.qmd
paper and parquets

library(tidyverse)
library(tinytex)
library(kableExtra)
library(knitr)
library(janitor)
library(kableExtra)
library(ggplot2)
library(xts)
library(tidyquant)

@@

@@

```{r}
#| label: tbl-SPXandPRKS
#| tbl-cap: Changes in Starbucks Stock Price from One Week Before Legal Action Against Workers United, the the Day it was Announced, to March 28th
#| echo: false

par(mfrow=c(2,1))
par(mar = c(0, 0, 0, 0))
plot(PRKS_Date,PRKS_Stocks, type="l", col="red" )
plot(PRKS_Date,SPX_Stocks, type="l", col="green" )

@@

>>>>

library(tidyverse)
library(tinytex)
library(kableExtra)
library(knitr)
library(janitor)
library(kableExtra)
library(ggplot2)
library(xts)
library(tidyquant)
library(arrow)

@@

cleaned_data_DJI <-read_parquet("../data/analysis_data/cleaned_data_DJI.parquet")

@@

@@

@tbl-SPXandPRKS
```{r}
#| label: tbl-SPXandPRKS
#| tbl-cap: Changes in Starbucks Stock Price from One Week Before Legal Action Against Workers United, the the Day it was Announced, to March 28th
#| echo: false

par(mfrow=c(2,1))
par(mar = c(0, 0, 0, 0))
plot(PRKS_Date,PRKS_Stocks, type="l", col="#0000c2" )
plot(PRKS_Date,SPX_Stocks, type="l", col="#FF5733" )

@tbl-DJIandNIKE
```{r}
#| label: tbl-DJIandNIKE
#| tbl-cap: Changes in Starbucks Stock Price from One Week Before Legal Action Against Workers United, the the Day it was Announced, to March 28th
#| echo: false

NIKE_DJI <-
  cleaned_data_DJI |>
  filter(between(date, as.Date('1991-07-18'), as.Date('1998-05-19')))

NIKE_Focus <-
  cleaned_data_NKE |>
  filter(between(Date, as.Date('1991-07-18'), as.Date('1998-05-19')))

DJI_Stocks <- NIKE_DJI$close
NIKE_Stocks <- NIKE_Focus$Close

NIKE_Date <- NIKE_Focus$Date

par(mfrow=c(2,1))
par(mar = c(0, 0, 0, 0))
plot(NIKE_Date,NIKE_Stocks, type="l", col="#0000c2" )
plot(NIKE_Date,DJI_Stocks, type="l", col="#FF5733" )
